Scheduling and Vectorization for MPC

### 2022-03-02 paper_SIMD.tex
Minor change to code example.

for j in range(0, N):
   res2 = PHI(res1, res3) // now 1-dim array
   tmp2[I] = ADD_SIMD(res2[I],B1[I,j])
   tmp3[I] = MUX_SIMD(tmp1[I,j], res2[I], tmp2[I])
   res3 = res2
   res3[I] = tmp3[I]
return res2
\end{verbatim}
}

>>>>

for j in range(0, N):
   res2 = PHI(res1, res3) // now 1-dim array
   tmp2[I] = ADD_SIMD(res2[I],B1[I,j])
   tmp3[I] = MUX_SIMD(tmp1[I,j], res2[I], tmp2[I])
   res3 = Update(res2, I, tmp3[I])
return res2
\end{verbatim}
}
